Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
Cleaning up

\section{Related Work} 
Here we will review previous algorithms for solving the optimal material assignment problem . We divide this review into two broad categories, optimizing for desired optical properties and optimizing for desired mechanical properties. Finally we will briefly review work done on modular shader languages as they have influenced our current work.

Optimizing and manufacturing objects with desired optical characteristics is a popular problem in computer graphics. Building objects which embed image in their caustics has been explored by Finch \textit{et al.} ~\shortcite{Finckh:2010} and Papas \textit{et al.}\shortcite{Marios:2011}. Optimization based approaches have also been employed to control the subsurface scattering of printed 3D models ~\cite{Hasan:2010}. These approaches have also been extended to optically decrypt hidden images ~\cite{Papas:2012}. Finally, optimal shadow casting surfaces have been produced which emulate a given set of input images ~\cite{Bermano:2012}.

@@

\autoref{tb:algorithms} shows the coordinate reduction method as well as the optimization scheme used in all cited works. A motivating observation for this research is that, despite different applications, these previous works share, not only a common methodology, but a set of common reduced coordinate components. These, in conjunction with (often off-the-shelf) optimization techniques form new material assignment algorithms. This suggests that one could find a small set of components that can be tied together to synthesize existing and new methods. Similar approaches have already proven useful for creating complex texture shading examples ~\cite{Cook1984}. Our goal in this paper is to produce an analogous mechanism for material assignment problems. 

@@

The overall contribution of our work is a flexible framework for the construction of material assignment algorithms. Our second contribution is the ``Reducer Network'',  a graphical data structure which describes both the geometric partitioning and material parameterization of  a given object. We couple this with a ``Tuner Network'' which automatically tunes the parameters of the Reducer Network to produce a fabricable object. Finally we provide an extensible API which utilizes these structures to produce numerous material assignment algorithms from a set of primitive operations.

@@

Computing material assignments at output device resolution is computationally intractable. Because of this, material assignments are computed  using a reduced representation. We specify this representation using a Reducer Network.  This structure is conceptually similar to those used in programmable shading systems (e.g. ~\cite{Cook1984}, Maya Shader Networks) . However these systems are primarily concerned with assigning known materials and textures to an object's surface whereas we are seeking a volumetric assignment of (as yet) unknown materials. In order to accomplish this task we build a directed, acyclic graph which has the object's surface geometry as its root node. We define two classes of nodes, geometry nodes and parameterization nodes. A geometry node takes a volumetric region as input and produces a partition of unity of this region as output. The leaf nodes of our graph are the parameterization nodes which associate a material assignment function of the form $\lambda\left(x,y,z,\theta\right)$ to an input volumetric region. Lambda can either output material parameters or a discrete material assignment for a spatial point $\left(x,y,z\right)$ given some parameters, here denoted by $\theta$. Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node. We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph however, for material assignment problems this is neither required nor desired.

 See \textbf{Figure \ref{fig:red1}} for an example of a Reducer Network. \note{Desai: Make figure 1}.\\
The sample Reducer Network can be constructed with the following pseudo-code.
%There are may be a better place to put the pseudo code
%\begin{program} can't figure out how to put it into a box
\begin{verbatim}
stratum->addInput(inputNode,0);
column->addInput(stratum, 0);
//add layered material to each column
for(ii =0;ii<column->getNOutput();ii++){
  layer = new LayeredMaterial(2);
  layer->addInput(column,ii);
}
uniform = new UniformMaterial(0);
uniform->addInput(stratum,1);
\end{verbatim}
%\caption{The Hello World! program in Java.}
%\end{program}

\begin{figure}[h]
\includegraphics[scale=0.3]{figure/redNetwork.pdf}
\caption{An Reducer Network we used to produce one of our results.
The input shape is sliced into two layers with the stratum partition node.
The top slice is then partitioned into columns. Each column is assigned
a stack of material layers.}
\label{fig:red1}
\end{figure}

\subsection{Tuners}
Tuner is an interface between a Reducer Node and an optimization algorithm.
A Tuner contains a pointer to a Reducer Node and a pointer to a generic optimization subroutine.
When a Tuner is linked to a Reducer Node, 
it can tune the free variables contained in the sub-tree rooted at that node.
\note{Desai: can you write this section, I don't know the details}
\subsection{Tuning the Reducer Network}
A Tuner initializes the optimization by querying the search space from its Reducer Node.
The Reducer Node computes the search space by traversing its sub-tree and collecting
free variables.
The search space specifies the number of free variables, the type of each free variable
(discrete or continuous) and the bounds of these variables.
With the search space specifies, the Tuner's optimization subroutine executes.
The optimization subroutine may ask for additional information such as
the error value of a variable assignment and the gradient. These queries are answered
with call-back functions set up by the Tuner before executing the optimization subroutine.
\subsection{Tuner Network}
\note{Desai: also this section :) }
For some fabrication problems, the best material to assign to a location
depends on the material assignment at nearby locations. 
Tuning the free variables as if they were independent usually yields
unsatisfactory results.
Therefore, we allow the tuner to share information according to 
a user-specified graph structure. 
This allows our framework to be interfaced with a wide range of existing
graph based optimization and inference algorithms.
For example, consider the Floyd–Steinberg dithering algorithm where the error of a pixel is distributed
to $4$ of its neighbors (right, lower left, down and lower right). 
The graph structure of this algorithm is illustrated in Figure~\ref{fig:tuner}.
The tuner is combined with the Reducer Network in Figure~\ref{fig:red1}.
A simplified view of the combined graph is shown in Figure~\ref{fig:combine}.
Executing each tuner in order is equivalent to running the Floyd–Steinberg dithering algorithm.

>>>>

\section{Related Work} 
Here we will review previous algorithms for solving the optimal material assignment problem . We divide this review into two broad categories, optimizing for desired optical properties and optimizing for desired mechanical properties. We conclude by commenting on the similarities between these approaches.

Optimizing and manufacturing objects with desired optical characteristics is a popular problem in computer graphics. Building objects which embed images in their caustics has been explored by Finch \textit{et al.} ~\shortcite{Finckh:2010} and Papas \textit{et al.}\shortcite{Marios:2011}. Optimization based approaches have also been employed to control the subsurface scattering of printed 3D models ~\cite{Hasan:2010}. These methods have also been extended to optically decrypt hidden images ~\cite{Papas:2012}. Finally, optimal shadow casting surfaces have been produced which emulate a given set of input images ~\cite{Bermano:2012}.

@@

\autoref{tb:algorithms} shows the coordinate reduction methods as well as the optimization schemes used in all cited works. A motivating observation for this research is that, despite different applications, these previous works share, not only a common methodology, but a set of common reduced coordinate components. These, in conjunction with (often off-the-shelf) optimization techniques form new material assignment algorithms. This suggests that one could find a small set of components that can be tied together to synthesize existing and new methods. Similar approaches have already proven useful for creating complex texture shading examples ~\cite{Cook1984}. Our goal in this paper is to produce an analogous mechanism for material assignment problems. 

@@

The overall contribution of our work is a flexible framework for the construction of material assignment algorithms. Our second contribution is the ``Reducer Network'',  a graphical data structure which describes both the geometric partitioning and material parameterization of  a given object. We couple this with a ``Tuner Network'' which automatically tunes the parameters of the Reducer Network to produce a fabricable object. Ultimately  we use these data structures to build an extensible, easy to use API which can produce numerous material assignment algorithms from a set of primitive operations.

@@

Computing material assignments at output device resolution is computationally inefficient. Because of this, material assignments are computed  using a reduced representation. We specify this representation using a Reducer Network.  This structure is conceptually similar to those used in programmable shading systems (e.g. ~\cite{Cook1984}, Maya Shader Networks) . However these systems are primarily concerned with assigning known materials and textures to an object's surface whereas we are seeking a volumetric assignment of (as yet) unknown materials. In order to accomplish this task we build a directed, acyclic graph which has the object's surface geometry as its root node. We define two classes of nodes, geometry nodes and parameterization nodes. A geometry node takes a volumetric region as input and produces a partition of unity of this region as output. The leaf nodes of our graph are the parameterization nodes which associate a material assignment function of the form $\lambda\left(x,y,z,\theta\right)$ to an input volumetric region. Lambda can either output material parameters or a discrete material assignment for a spatial point $\left(x,y,z\right)$ given some parameters, here denoted by $\theta$. Because the network describes a nested set of partitions of unity we can efficiently perform material queries by passing a query point through the network until it arrives at a parameterization node. We note that Reducer Networks do not inherently enforce material continuity between disjoint regions in the graph, however, for material assignment problems this is neither required nor desired.

\autoref{fig:red1} shows an example Reducer Network which can be constructed with the following pseudo-code.
%There are may be a better place to put the pseudo code
%\begin{program} can't figure out how to put it into a box
\begin{verbatim}
stratum->addInput(inputNode,0);
column->addInput(stratum, 0);
//add layered material to each column
for(ii =0;ii<column->getNOutput();ii++){
  layer = new LayeredMaterial(2);
  layer->addInput(column,ii);
}
uniform = new UniformMaterial(0);
uniform->addInput(stratum,1);
\end{verbatim}
%\caption{The Hello World! program in Java.}
%\end{program}

\begin{figure}[h]
\includegraphics[scale=0.3]{figure/redNetwork.pdf}
\caption{A Reducer Network used to produce one of our results.
The input geometry is sliced into two layers with the stratum partition node.
The top slice is then partitioned into columns. Each column is assigned
a stack of material layers.}
\label{fig:red1}
\end{figure}

\subsection{Tuners}
We define tuners as an abstract interface between a Reducer Node and an optimization algorithm.  Specifically a tuner is comprised of an optimization scheme, an error metric and a goal. Each tuner is attached to a specific geometric node in the Reducer Network. It then acts to optimize, or tune, the free variables associated with the subtree rooted at this node. One can think of this as a self-tuning shader network.  This organizational structure allows us to easily optimize subdomains of our object using different tuners. We provide a mechanism for scheduling tuner execution thus allowing both serial and parallel processing. \note{Add a figure showing an example tuner}
\subsection{Tuning the Reducer Network}
A Tuner initializes an optimization by querying the search space from its Reducer Node.
The Reducer Node computes the search space by traversing its sub-tree and collecting
free variables. The search space specifies the number of free variables, the type of each free variable
(discrete or continuous) and the bounds of these variables. With the search space specified, the Tuner's optimization subroutine executes. The optimization subroutine may ask for additional information such as
the error value of a variable assignment and the gradient. These queries are answered
with call-back functions set up by the Tuner before executing the optimization subroutine. We note that gradient computation of our material function $\lambda$ can be performed by efficiently traversing the Reducer Network.
\subsection{Tuner Network}
For many fabrication problems, tuners cannot act in isolation. For instance,  occasionally the best material at a given point in space is dependent upon the material assignment at nearby locations.  Tuning the free variables as if they were independent usually yields unsatisfactory results. Therefore, we allow the tuner to share information according to a user-specified graph structure.  This allows our framework to be interfaced with a wide range of existing graph based optimization and inference algorithms. For example, consider the Floyd–Steinberg dithering algorithm where the error of a pixel is distributed
to $4$ of its neighbors (right, lower left, down and lower right).  The graph structure of this algorithm is illustrated in Figure~\ref{fig:tuner}. The tuner is combined with the Reducer Network in Figure~\ref{fig:red1}. A simplified view of the combined graph is shown in Figure~\ref{fig:combine}. Executing each tuner in order is equivalent to running the Floyd–Steinberg dithering algorithm.
